### 2021-11-07 NSF2021/Description/specificaim1.tex
fixed citations in background, SA1

The proposed research aims to provide fundamental insight into the
self-assembly dynamics of amphiphilic particles. These results will
facilitate optimal design of smart materials by tuning the geometry and
properties of the amphiphilic particles.
The theories presented in Background pertain to one-dimensional problems
for a water region separating parallel surfaces.
In two and higher dimensions, there 
is an explosion of possible phenomena.
Thus, Specific Aim 1 concerns  improving on established models and theory.

@@

As an illustration, in one-dimension the minimizer in \eqref{eq:free_energy} 
solves $-u''(x) + f'(u(x)) = 0$ for $0 < x < b$, $u(0) = u_0(0),$ $u(b) = u_0(b)$ 
and the free energy takes the form $F(b)$
where $b$ is the  distance of separation between the hydrophobic surfaces.
The hydrophobic force $-F'(b)$ the variation of free energy with respect to $b$  \cite{ErLjCl89, GoKl94}.

In two and higher spatial dimensions, the situation is more complicated.
That is because the particles rotate and translate individually.  Here, the 
minimizer  in \eqref{eq:free_energy}  satisfies 
\begin{equation}
\label{eq:SL}
-\Delta u + f'(u) = 0  \text{ in } \Omega,\quad u = u_0  \text{ on } \partial \Omega.
\end{equation}
The hydrophobic forces are torques are
\begin{equation}
  \label{eq:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu) \dif s.
\end{equation}
where the surface force density 
\begin{align}
  \label{eq:stress}
\mathbf{T}
= C \left[ f(u) \mathbf{I} +  \left(|\nabla
  u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)\right]
\end{align}
comes from the variation of free energy with respect to particle 
position and orientation~\cite{Bandle2015, Schiffer1954, Grinfeld2010}. 
The remaining part of the force comes from excluded volume repulsion. 
The density \label{eq:stress}  was introduced
by~\cite{Fu20} and is responsible for forming particle aggregates that
sequester their hydrophobic surface regions (Figure \ref{fig:figure0}b).

\subsection{Janus-particle self-assembly} 
The PI will collaborate with Dr. Bradley in the Department of 
Polymer and Engineering Science at the University of Massachusetts Amherst
on numerical and experimental investigations
of synthesis and assembly of soft matter materials.
Dr. Bradley's lab specializes in synthesizing multiphasic and anisotropic colloids.
Applications in this area enables include cargo-carrying capacity, 
catalytic activity, or stimuli-responsive shape-change to amplify colloid utility for a wide 
range of  spanning environmental remediation to drug delivery. 
The main challenge is the ability decouple particle surface properties, 
which control particle-particle and particleiiinterface interactions, 
from auxiliary functions, such as catalytic or cargo-carrying capacities
\cite{}.

@@

Our next steps are to determine if the phenomenon we report are robust.
This involves categorizing all possible the self assembly behavior
and assessing the sensitivity of morphologies to boundary condition positionally
and particle geometry.  At the same time, we can  
translate phenomenological parameters parameters
of the model in to contact angles. In Specific Aim 3, we discuss how to include 
surface charge as this is one of the main surface properties that must be decoupled.
In future studies, we will also include liquid crystal background flows.

\subsection{Hydrophobic forces as capillary wetting} 
The measured hydrophobic attraction follows an exponential function
in the 10 to 100 nanometer range of separation.  Below 10 nm, there 
is an amplification of force and the attraction follows a much steeper 
force law \cite{Lietal05}.

@@

\textbf{How will we know the results are accurate?}
The experimental data on hydrophobic attraction between 
hydrocarbon coated mica cylinders well-established. 
The literature contains data for a number of solvents and hydrocarbon species.
Our numerical experiments will choose particle geometries that replicate the 
experimental setups, mainly apposing hydrocarbon coated cylinders. 
We will directly compare the numerical attraction data with the measurements.
Some of the model parameters, like $C$ and  $f''(u_1)$, directly connect 
to long-range decay lengths and energy cost of creating hydrophobic-water
interfaces with established ranges of values. Other parameters, like the well-structure,
are fit to the measured data. 
These base-line simulations will allow us to move on to simulating
colloidal suspensions.

>>>>

The proposed research aims to provide fundamental insight into the
self-assembly dynamics of amphiphilic particles. These results will
facilitate optimal design of smart materials by tuning the geometry and
properties of the amphiphilic particles.
The theories presented in Background pertain to one-dimensional problems
for a water region separating parallel surfaces.In two and higher
dimensions, there is an explosion of possible phenomena. Thus, Specific
Aim 1 concerns improving on established models and theory.

@@

As an illustration, in one-dimension the minimizer in
\eqref{eq:free_energy} solves $-u''(x) + f'(u(x)) = 0$ for $0 < x < b$,
$u(0) = u_0(0),$ $u(b) = u_0(b)$ and the free energy takes the form
$F(b)$ where $b$ is the  distance of separation between the hydrophobic
surfaces. The hydrophobic force $-F'(b)$ the variation of free energy
with respect to $b$  \cite{ErLjCl89, GoHaKo94}.

In two and higher spatial dimensions, the situation is more complicated.
That is because the particles rotate and translate individually.
Here, the minimizer  in \eqref{eq:free_energy} satisfies 
\begin{equation}
\label{eq:SL}
-\Delta u + f'(u) = 0  \text{ in } \Omega,\quad u = u_0
\text{ on } \partial \Omega.
\end{equation}
The hydrophobic forces are torques are
\begin{equation}
  \label{eq:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
    \quad 
    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
    ({\bf T} \cdot \nnu) \dif s.
\end{equation}
where the surface force density 
\begin{align}
  \label{eq:stress}
\mathbf{T}
= C \left[ f(u) \mathbf{I} +  \left(|\nabla
  u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)\right]
\end{align}
comes from the variation of free energy with respect to particle 
position and orientation~\cite{Bandle2015, Schiffer1954, Grinfeld2010}. 
The remaining part of the force comes from excluded volume repulsion. 
The density \label{eq:stress}  was introduced
by~\cite{Fu2018_SIAM} and is responsible for forming particle aggregates that
sequester their hydrophobic surface regions.

\subsection{Janus-particle self-assembly} 
The PI will collaborate with Dr. Bradley in the Department of 
Polymer and Engineering Science at the University of Massachusetts Amherst
on numerical and experimental investigations
of synthesis and assembly of soft matter materials.
Dr. Bradley's lab specializes in synthesizing multiphasic and anisotropic
colloids. Applications in this area enables include cargo-carrying capacity, 
catalytic activity, or stimuli-responsive shape-change to amplify colloid
utility for a wide range of  spanning environmental remediation to drug
delivery. The main challenge is the ability decouple particle surface properties, 
which control particle-particle and particleiiinterface interactions, 
from auxiliary functions, such as catalytic or cargo-carrying capacities.

@@

Our next steps are to determine if the phenomenon we report are robust.
This involves categorizing all possible the self assembly behavior and
assessing the sensitivity of morphologies to boundary condition
positionally and particle geometry.  At the same time, we can translate
phenomenological parameters of the model in to contact angles. In Specific
Aim 3, we include surface charge as this is one of the main surface
properties that must be decoupled. In future studies, we will also include
liquid crystal background flows.

\subsection{Hydrophobic forces as capillary wetting} 
The measured hydrophobic attraction follows an exponential function
in the 10 to 100 nanometer range of separation.  Below 10 nm, there 
is an amplification of force and the attraction follows a much steeper 
force law \cite{Lin2005}.

@@

\textbf{How will we know the results are accurate?}
The experimental data on hydrophobic attraction between 
hydrocarbon coated mica cylinders well-established. 
The literature contains data for a number of solvents and hydrocarbon species.
Our numerical experiments will choose particle geometries that replicate the 
experimental setups, mainly apposing hydrocarbon coated cylinders. 
We will directly compare the numerical attraction data with the measurements.
Some of the model parameters, like $C$ and  $f''(u_1)$, directly connect 
to long-range decay lengths and energy cost of creating hydrophobic-water
interfaces with established ranges of values. Other parameters, like the
well structure, are fit to the measured data. These base-line simulations
will allow us to move on to simulating colloidal suspensions.
